Project Report:\\\LARGE \bf Stereo Matching using Graphcut-based Optimization

### 2014-04-15 report/paper.tex
report

\title{\LARGE \bf
Stereo Matching using Graphcut-based Optimization}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\end{abstract}

@@

\bibliographystyle{ieeetr} 
\bibliography{refs}

>>>>

\title{Project Report:\\\LARGE \bf
Stereo Matching using Graphcut-based Optimization}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure*}[t]
        \centering
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{imgs/l4.png}
                \caption{"Art" Color image}
                \label{fig:trees}
        \end{subfigure}%
                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{imgs/disp4.png}
                \caption{Ground Truth}
                \label{fig:farm}
        \end{subfigure}
                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{imgs/l4disparity-expansion.png}
                \caption{$\alpha$-expansion}
                \label{fig:farm}
        \end{subfigure}
                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{imgs/l4disparity-swap.png}
                \caption{$\alpha\beta$-swap}
                \label{fig:farm}
        \end{subfigure}
                        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{imgs/l4disparity-expansion-sub.png}
                \caption{$\alpha$-expansion - subpixel accuracy}
                \label{fig:farm}
        \end{subfigure}
                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{imgs/l4disparity-swap-sub.png}
                \caption{$\alpha\beta$-swap - subpixel accuracy}
                \label{fig:farm}
        \end{subfigure}
        \caption{Disparity image for the "Art" dataset using the both $\alpha\beta$-swap and $\alpha$-expansion with pixel and subpixel accuracies.}
        \label{fig:realmaps}
\end{figure*}

\begin{figure*}[t]
        \centering
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{imgs/l2.png}
                \caption{"Wood1" Color image}
                \label{fig:trees}
        \end{subfigure}%
                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{imgs/disp2.png}
                \caption{Ground Truth}
                \label{fig:farm}
        \end{subfigure}
                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{imgs/l2disparity-expansion.png}
                \caption{$\alpha$-expansion}
                \label{fig:farm}
        \end{subfigure}
                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{imgs/l2disparity-swap.png}
                \caption{$\alpha\beta$-swap}
                \label{fig:farm}
        \end{subfigure}
                        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{imgs/l2disparity-expansion-sub.png}
                \caption{$\alpha$-expansion - subpixel accuracy}
                \label{fig:farm}
        \end{subfigure}
                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3\textwidth}
                \centering
                \includegraphics[width=\textwidth]{imgs/l2disparity-swap-sub.png}
                \caption{$\alpha\beta$-swap - subpixel accuracy}
                \label{fig:farm}
        \end{subfigure}
        \caption{Disparity image for the "Wood1" dataset using the both $\alpha\beta$-swap and $\alpha$-expansion with pixel and subpixel accuracies.}
        \label{fig:realmaps}
\end{figure*}

In this project we developed a stereo matching system based on graph-cut optimization framework \cite{boykov2001fast}. In stereo matching problem, 2 images taken from 2 cameras that are in the same hozirontal like The input to the system is a pare of images

\section{Graphcut-based Optimization}
\section{Stereo Matching}
\section{Experiments and Results}
\bibliographystyle{ieeetr} 
\bibliography{refs}
